[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting and intermittent phase-locking

### 2016-08-25 article/detorakis-2016.tex
4th review - corrections

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting
        and intermittent phase-locking
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
\usepackage{array}
\usepackage[export]{adjustbox}

@@

@@

\date{\vspace{-5mm}
    \sffamily \small \href{mailto:gdetorak@uci.edu}{gdetorak@uci.edu}}

@@

This work introduces a reference implementation of a neuron model for
thalamocortical relay neurons, proposed by X-J Wang, \cite{wang:1994}.
The model is conductance-based and takes advantage of an interplay between
a T-type calcium current and a non-specific cation sag current and thus, it
is able to generate spindle and delta rhythms. Another feature of this model
is the presence of an intermittent phase-locking phenomenon where action 
potentials of sodium take place in a non-periodic manner, despite the fact
that they are phase-locked to the periodic input current. Finally, the model
is capable of generating tonic spike patterns. The source code of
reference implementation is written in Python (Numpy, Scipy, Matplotlib,
and Scikit-image).

@@

In this section, a detailed description of the model is given following 
the paradigm of Nordlie et al, \cite{nordlie:2009}. To this end description of
the model, equations, parameters, and inputs are given in the form of tables.

Table~\ref{Table:1} provides a description of the model, Table~\ref{Table:2}
provides information about simulations duration and temporal integration time
steps, Table~\ref{Table:3} gives a glimpse of the input signals used in this
work. Table~\ref{Table:4} introduces the equations of the model and finally 
Table~\ref{Table:5} summarizes all the parameters for each figure (simulation).
The neuron model is conductance-based consisting of four differential equations
describing the dynamics of membrane potential and the kinetics of a T-Type
calcium current, a Sag current channel and a Potassium channel. The rest
currents are described by algebraic equations.
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- one neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Hodgkin-Huxley conductance-based \\\rowcolor{Gray}
        Channel Models & \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or periodic rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, channels activation, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{Table:1}
\end{table}
 %%  
The reference implementation has been done in a Python class (Python $3.5.1$)
along with Numpy (version $1.10.4$), Scipy (version $0.17.0$), Matplotlib
($1.5.1$) and Scikit-image (version $0.12.3$). The numerical integration
has been done using the \emph{ode} method of Scipy \emph{integrate} package.
Three different methods have been tested in this work (\emph{dopri5}, 
\emph{Adams}, \emph{BDF}, \cite{ascher:1998}). \emph{Dopri5} is the closest
numerical method to the one used by \cite{wang:1994} (fifth-order adaptive 
size Runge-Kutta method). \emph{BDF} and \emph{Adams} provide similar numerical
results as the first one, but they are faster. In the current implementation
of \cite{wang:1994} the user has the option to choose one of the three methods
at the stage of class instantiating. All three aforementioned methods have
been tested by comparing, spike times, amplitudes and the coefficient
of variation using as threshold value $0\, \Rm{mV}$. Spike events were
overlapping, and $CV \simeq 3.5$ for all three methods. A difference found 
in the amplitude of spikes generated by the three methods. Figure~\ref{Fig:1}
shows two histograms of error distribution (error is defined to be the
absolute difference of spike amplitude between two methods). Top histogram 
depicts a distribution of differences in amplitude between \emph{dopri5} 
and \emph{Adams} methods (gray color). The bottom histogram illustrates the 
distribution of amplitude differences between \emph{dopri5} and \emph{BDF}
methods (red color). In the rest of the article all the results have been 
produced by using the \emph{Adams} method.
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ccc}
        \thickhline
        \multicolumn{3}{c}{Simulation Time} \\ \thickhline
        Figure & Simulation Time ($\Rm{s}$) & Integration Step ($\Rm{ms}$) \\ 
        \rowcolor{LightGray}
        $1$ & $6$ & $0.05$ \\ \rowcolor{Gray}
        $2$ & $15\times period$, $5$ & $0.05$ \\ \rowcolor{LightGray}
        $3$ & $6$ & $0.05$ \\ \rowcolor{Gray} 
        $4$ & $1.5$, $1$, $1$ & $0.05$ \\ \rowcolor{LightGray} 
        $5$ & $5$ & $0.05$  \\ \rowcolor{Gray} 
        $6$ & $5$ & $0.05$  \\ \rowcolor{LightGray} 
        $7$ & $40$, $20$ & $0.05$  \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Time}}
    \label{Table:2}
\end{table}
%%

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure1.pdf}
    \caption{{\bfseries \sffamily Amplitude difference distribution} 
    {\bfseries \sffamily Top histogram} depicts the distribution of differences
    in spikes amplitudes between \emph{dopri5} and \emph{Adams} integration
        methods of Scipy \emph{integrate} package (black color). 
    {\bfseries \sffamily Bottom histogram} illustrates the distribution of
    differences in spikes amplitudes between \emph{dopri5} and \emph{BDF}
    methods (red color). In both cases the number of bins is $30$. 
    }
    \label{Fig:1}
\end{figure}

@@

%%
\begin{landscape}
\begin{table}[!htbp]
    \centering
    \begin{tabular}{cccccccc}
        \thickhline
        \multicolumn{8}{c}{Model Parameters} \\\thickhline
        Figure & $V_0\, (\Rm{mV})$ & $g_T\, (\Rm{mS/cm^2})$ & $\theta_h\,
        (\Rm{mV})$ & $k_h\, (\Rm{mV^{-1}})$ & $\sigma_{Na}\, (\Rm{mV})$ &
        $g_L\, (\Rm{mS/cm^2})$ & $V_L\, (\Rm{mV})$ \\\rowcolor{LightGray}
        \thickhline
        $1$ & $-74$ & $1$ & $-79$ & $-5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $2$ & $-74$ & $1$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\\rowcolor{LightGray}
        $3$ & $-74$ & $0.3$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $4$ & $-72$/$-64$ & $1.0$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{LightGray}
        $5$ & $-74$ & $0.3$ & $-75$ & $5$ & $6$ & $0.08$ & $-70$ \\\rowcolor{Gray}
        $6$ & $-74$ & $1$/$0.7$ & $-79$ & $5$ & $6$ & $0.1$/$0.04$ & $-70$ \\\rowcolor{LightGray}
        $7$ & $-72$ & $0.3$/$0.25$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\
        \thickhline
        \multicolumn{8}{l}{Common Parameters} \\\rowcolor{Gray}
        \multicolumn{8}{c}{$C_m = 1\, \Rm{\mu F/cm^2}$, $\phi_h = 2$,
        $V_{\Rm{Ca}} = 120\, \Rm{mV}$, $\phi_H = 1$, $g_h = 0.04\,
        \Rm{mS/cm^2}$, $V_h = -40\, \Rm{mV}$, $g_{\Rm{K}} = 30\, \Rm{mS/cm^2}$,
        $V_{\Rm{K}} = -80\, \Rm{mV}$, $g_{\Rm{Ca}} = 42\, \Rm{mS/cm^2}$} \\\rowcolor{Gray}
        \multicolumn{8}{c}{$V_{\Rm{Ca}} = 55\, \Rm{mV}$, $\phi_{n} = 28.5$,
        $\sigma_{\Rm{K}} = 10\, \Rm{mV}$, $V_{\Rm{Na(P)}} = 55\, \Rm{mV}$,
        $\sigma_{\Rm{Na(P)}} = -5\, \Rm{mV}$, $g_{\Rm{Na(P)}} = 9 \,
        \Rm{mS/cm^2}$}
        \\\thickhline
    \end{tabular}
    \caption{\bfseries \sffamily Simulation Parameters}
    \label{Table:5}
\end{table}
\end{landscape}
%%

@@

We simulated the model described in Table~\ref{Table:4} using the parameters
given in Table~\ref{Table:5} and the corresponding input (see 
Table~\ref{Table:3}). First, we examined what is the response of the reference 
implementation to rhythmic hyperpolarization. In \cite{wang:1994} this is 
illustrated in Fig~$1$\footnote{From now and then original article's figures
    will be referred as Fig}. 
Thus, we applied a periodic current pulse of $-1\,\Rm{\mu A/cm^2}$ amplitude at
several different frequencies ($\frac{1}{P_0}$ is the frequency in $\Rm{Hz}$
and $P_0$ is the corresponding period in $\Rm{ms}$) ranging from 
$0.1\,\Rm{Hz}$ to $15\,\Rm{Hz}$ with a resolution (discretization) of $100$ 
points. The same number of samples used for discretizing the duration of the
pulse for each frequency.

Upper panel shows two different simulations of the reference implementation at
specific frequencies ($5,\, 0.5\, \Rm{Hz}$) and ratios $p/P_0$ ($0.6, 0.6$),
respectively (following the upper panels of Fig~$1$ in \cite{wang:1994}).
These panels are comparable to the ones presented in \cite{wang:1994} and the 
timescales are exactly the same ($400\, \Rm{ms}$ for the left sub-panel and
$4\, \Rm{s}$ for the second one). However, numbers regarding pulse ON duration
($p$) in Fig~$1$ of \cite{wang:1994} are not correct. For instance, take the
frequency to be $\frac{1}{P_0} = 5\, \Rm{Hz}$ and $\frac{p}{P_0} = 0.6$ then
the pulse ON duration must be $p = 120\, \Rm{ms}$ and not $160\, \Rm{ms}$.

Bottom panel illustrates the total results of the $100 \times 100$ simulations
we ran.  In order to create this figure, we counted the number of spikes
generated per pulse, both supra-threshold and sub-threshold, and then we 
computed the mean (this procedure is not described in a solid way in
\cite{wang:1994}, however it is described in \cite{mccormick:1990}).  
This figure is different from \cite{wang:1994}, where the shaded area that 
contains an average number of spikes below $1.0$ (but not zero) is larger
than in \cite{wang:1994}. Unfortunately, information regarding Fig~$1$
is limited in \cite{wang:1994} in order to be able to follow a specific recipe
and try to reproduce exactly the same figure.

%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure2.pdf}
    \caption{{\bfseries \sffamily Responses to rhythmic hyperpolarizations.}
        We stimulate the model with a periodic pulse with varying frequency
        $\frac{1}{P_0}$ in $[0.1, 15]\, \Rm{Hz}$ and ON pulse duration $p$. 
        {\bfseries \sffamily Upper panels} Show the results of two specific
        simulations out of the $100 \times 100$ we ran in total. The blue 
        curve illustrates a case where bursts of four spike take place when
        frequency is $\frac{1}{P_0} = 5\, \Rm{Hz}$ and $\frac{p}{P_0} = 0.6$.
        Black 
        curve depicts a case of two spikes bursts. In this case the frequency
        is $\frac{1}{P_0} = 0.5\, \Rm{Hz}$ and $\frac{p}{P_0} = 0.6$.
        {\bfseries \sffamily Bottom panel} shows a range of frequencies
        $\frac{1}{P_0}$ from $0.1\, \Rm{Hz}$ to $15\, \Rm{Hz}$ versus the ratio
        $\frac{p}{P_0}$ in range $[0, 1]$. Numbers indicate the average number
        of spikes per pulse. }
    \label{Fig:2}
\end{figure}
%%

Then we tested the transition from subthreshold to bursting oscillations via 
chaos. Therefore, we used a steady current varying only its amplitude keeping
all the other parameters fixed. We used eight different values (exactly the
same as in \cite{wang:1994}),
$$I_{\text{app}} =
3.0, 0.0, -0.45, -0.455, -0.47, -0.55, -0.6, -0.8, -1.3, -1.4, -2.0\, 
\Rm{\mu A /cm^2}.$$ Results are depicted in Figure~\ref{Fig:3}. This figure
corresponds to Fig~$3$ of \cite{wang:1994}. In this case, there was no
difference between the reference implementation and the original one. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.\textwidth]{figs/Figure3.pdf}
    \caption{{\bfseries \sffamily Dynamic behavior of neuron.} Here we
    simulate the model with parameters given in Table~\ref{Table:5}. The
    only parameter that varies from panel to panel in this figure is the
    external current $I_{\text{ext}}$. These results correspond to Fig~$3$ 
    of \cite{wang:1994}.}
    \label{Fig:3}
\end{figure}
%%

The next simulation we performed reproduces results related to hysteresis as
in Fig~$4$ of \cite{wang:1994}. First, we run a simulation where the input 
current $I_{ext}$ varied from $-0.433\, \Rm{\mu A / cm^2}$ to $-0.55 \mu A /cm^2$.
At every iteration, we detected if there is subthreshold and/or suprathreshold 
activity in the membrane voltage trace. Thus we created the hysteresis diagram
given in Figure~\ref{Fig:4}, top panel. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure4.pdf}
    \caption{{\bfseries \sffamily Hysteresis near the transition from the
    subthreshold to bursting oscillation.} {\bfseries \sffamily First panel:}
    Hysteresis diagram indicates a coexistence of bursting and subthreshold 
    activity. {\bfseries \sffamily Second panel:} Bistability example
    shows how the same system can produce either subthreshold activity (black
    curve) or burst activity (gray curve). {\bfseries \sffamily Third 
    panel:} shows the activation of $H$ for the same simulation as in the upper
    panel. {\bfseries  \sffamily Fourth panel:} Input to the model for
    this simulation is a brief current pulse at $0.25\, \Rm{\mu A /cm^2}$
    (black curve) and $-1.2\, \Rm{\mu A/cm^2}$ (gray curve) followed by a
    steady current at $-0.47\, \Rm{\mu A/cm^2}$ for both simulations. }
    \label{Fig:4}
\end{figure}
%%
In addition, we tested the bistability of the current model using the same 
protocol as in \cite{wang:1994}. According to that protocol, we first apply 
a brief pulse (for $100\, \Rm{ms}$) of $0.25\, \Rm{\mu A /cm^2}$ and
$-1.2\, \Rm{\mu A/cm^2}$ followed by a steady current at $-0.47\, 
\Rm{\mu A /cm^2}$. This causes the state of the model to switch from a purely 
subthreshold activity pattern to a mixed sub- and suprathreshold activity
pattern. The results are given in Figure~\ref{Fig:4}, right panel.

Another interesting behavior of the model is the development of a ``spiral''
chaos (see Fig~$6$ in \cite{wang:1994}). The reference implementation is 
capable of generating similar behavior as Figure~\ref{Fig:5} shows. In order
to get these results we applied a constant external current with an amplitude
of $-0.95\, \Rm{\mu A / cm^2}$. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.6\textwidth]{figs/Figure5.pdf}
    \caption{{\bfseries \sffamily ``Spiral Chaos''.} In this Figure
    we show that the model is capable of generating ``spiral chaos''
    as it has been shown in Fig~$6$ in \cite{wang:1994}.
    The external current in this simulation is constant ($-0.95\Rm{\mu A/cm^2}$). 
    {\bfseries \sffamily Top panel} shows the phase portrait of the 
    membrane potential and the Sag current ($V$ vs $h$).
    {\bfseries \sffamily Middle panel} illustrates the membrane potential ($V$)
    and, the {\bfseries \sffamily bottom panel} shows the $h$ current over time.}
    \label{Fig:5}
\end{figure}
%%

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\usepackage{bm,array}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] Multiple dynamical modes of thalamic relay neurons: rhythmic bursting
        and intermittent phase-locking
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
\usepackage{array}
\usepackage[export]{adjustbox}

@@

\newcolumntype{C}{>{\centering\arraybackslash}p{3.5em}}

@@

\date{\vspace{-5mm}
    \sffamily \small \href{mailto:gdetorak@uci.edu}{gdetorak@uci.edu} \\
    \sffamily \small \href{mailto:gdetor@protonmail.com}{gdetor@protonmail.com}}

@@

The present paper replicates a neuron model for thalamocortical relay neurons,
proposed by X-J Wang, \cite{wang:1994}. The model is conductance-based and 
takes advantage of the interplay between a T-type calcium current and a 
non-specific cation sag current and thus, it is able to generate spindle
and delta rhythms. Another feature of this model is the presence of an
intermittent phase-locking phenomenon where action potentials of sodium take
place in a non-periodic manner, despite the fact that they are phase-locked to
the periodic input current. Finally, the model is capable of generating tonic
spike patterns. The source code for replicating Wang's model is written in
Python (Numpy, Scipy, Matplotlib, and Scikit-image).

@@

In this section, a detailed description of the model is given following 
the paradigm of Nordlie et al, \cite{nordlie:2009}. To this end, a description
of the model's equations, parameters, and inputs are given in the form of
tables.

Table~\ref{Table:1} and~\ref{Table:2} provide a description of the model and 
information about simulations duration and time steps, respectively. 
Table~\ref{Table:3} gives a glimpse of the input signals used in this work and
Table~\ref{Table:4} introduces the equations of the model. Table~\ref{Table:5}
summarizes all the parameters used in this work.

The neuron model is conductance-based, consisting of four differential
equations describing the dynamics of membrane potential and the kinetics of
a T-Type calcium current, a Sag current channel and a Potassium channel. The
rest of the currents are described by algebraic equations.
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- one neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Hodgkin-Huxley conductance-based \\\rowcolor{Gray}
        Channel Models & \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or periodic rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, channels activation, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{Table:1}
\end{table}
 %%

Before proceeding to the simulations we introduce a few details regarding 
the source code and the integration method which should be accurate and fast
enough. The implementation is a Python class (Python $3.5.1$), which uses
Numpy (version $1.10.4$), Scipy (version $0.17.0$), Matplotlib
($1.5.1$) and Scikit-image (version $0.12.3$) packages. The numerical
integration is carried out using the \emph{ode} method of Scipy 
\emph{integrate} package. Three different methods were tested in this work 
(\emph{dopri5}, \emph{Adams}, \emph{BDF}, \cite{ascher:1998}). \emph{Dopri5}
is the closest numerical method to the one used by \cite{wang:1994}
(fifth-order adaptive size Runge-Kutta method). The user of the present 
implementation can choose one of the three methods at the stage of class
instantiating. For all three methods we measured spike times, membrane
potential amplitudes and the coefficient of variation using as threshold value
$0\, \Rm{mV}$. We found that spike event times for \emph{dopri5}, \emph{Adams}
and \emph{BDF} coincide and they all have the same $CV \simeq 2.3608$. 
However, the amplitude of membrane potential was different. Figure~\ref{Fig:1}
{\bfseries \sffamily A} shows the membrane potential (in $\Rm{mV}$) produced by
\emph{dopri5} plotted against the membrane potential generated by \emph{Adams}
method. Figure~\ref{Fig:1} {\bfseries \sffamily B} shows the membrane potential
of a simulation using \emph{dopri5} against another using \emph{BDF}. The 
\emph{Adams} method has less differences in amplitude from \emph{dopri5} 
than \emph{BDF}. Therefore, we decided to use the \emph{Adams} method 
since it runs faster than \emph{dopri5}. 
%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ccc}
        \thickhline
        \multicolumn{3}{c}{Simulation Time} \\ \thickhline
        Figure & Simulation Time ($\Rm{s}$) & Integration Step ($\Rm{ms}$) \\ 
        \rowcolor{LightGray}
        $1$ & $6$ & $0.05$ \\ \rowcolor{Gray}
        $2$ & $15\times period$, $5$ & $0.05$ \\ \rowcolor{LightGray}
        $3$ & $6$ & $0.05$ \\ \rowcolor{Gray} 
        $4$ & $1.5$, $1$, $1$ & $0.05$ \\ \rowcolor{LightGray} 
        $5$ & $5$ & $0.05$  \\ \rowcolor{Gray} 
        $6$ & $5$ & $0.05$  \\ \rowcolor{LightGray} 
        $7$ & $40$, $20$ & $0.05$  \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulations Time}}
    \label{Table:2}
\end{table}
%%

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{figs/Figure1.pdf}
    \caption{{\bfseries \sffamily Amplitude differences} The membrane potential
    ($\Rm{mV}$) is generated using \emph{dopri5} integration method and is 
    plotted against ({\bfseries \sffamily A}) the one generated by \emph{Adams}
    method and ({\bfseries \sffamily B}) \emph{BDF} method.}
    \label{Fig:1}
\end{figure}

@@

%%
\begin{table}[!htbp]
    \centering
    %\begin{tabular}{cccccccc}
    \begin{tabular}{CCCCCCCC}
        \thickhline
        \multicolumn{8}{c}{Model Parameters} \\\thickhline
        Figure & \begin{tabular}[x]{@{}c@{}} $V_0$ \\ $(\Rm{mV})$ \end{tabular}
            & \begin{tabular}[x]{@{}c@{}} $g_T$ \\ $(\Rm{mS/cm^2})$ \end{tabular}
            & \begin{tabular}[x]{@{}c@{}} $\theta_h$ \\ $(\Rm{mV})$ \end{tabular}& 
            \begin{tabular}[x]{@{}c@{}} $k_h$ \\ $(\Rm{mV^{-1}})$ \end{tabular}&
            \begin{tabular}[x]{@{}c@{}} $\sigma_{Na}$ \\ $(\Rm{mV})$ \end{tabular}&
            \begin{tabular}[x]{@{}c@{}} $g_L$ \\ $(\Rm{mS/cm^2})$ \end{tabular}&
            \begin{tabular}[x]{@{}c@{}} $V_L$ \\ $(\Rm{mV})$ \end{tabular}\\\rowcolor{LightGray}
        \thickhline
        $1$ & $-74$ & $1$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $2$ & $-74$ & $0.3$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\\rowcolor{LightGray}
        $3$ & $-74$ & $1$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{Gray}
        $4$ & $-72$/$-64$ & $1.0$ & $-79$ & $5$ & $6$ & $0.12$ & $-70$ \\\rowcolor{LightGray}
        $5$ & $-74$ & $1.0$ & $-75$ & $5$ & $6$ & $0.08$ & $-70$ \\\rowcolor{Gray}
        $6$ & $-74$ & $1$/$0.7$ & $-79$ & $5$ & $6$ & $0.12$/$0.04$ & $-70$ \\\rowcolor{LightGray}
        $7$ & $-72$ & $0.3$/$0.25$ & $-81$ & $6.25$ & $3$ & $0.1$ & $-72$ \\
        \thickhline
        \multicolumn{8}{l}{Common Parameters} \\\rowcolor{LightGray}
        \thickhline
        \multicolumn{8}{p{36.5em}}{
        $C_m = 1\, \Rm{\mu F/cm^2}$, $\phi_h = 2$,
        $V_{\Rm{Ca}} = 120\, \Rm{mV}$, $\phi_H = 1$, $g_h = 0.04\,
        \Rm{mS/cm^2}$, $V_h = -40\, \Rm{mV}$,         
        $g_{\Rm{K}} = 30\, \Rm{mS/cm^2}$,
        $V_{\Rm{K}} = -80\, \Rm{mV}$, $g_{\Rm{Na}} = 42\,\Rm{mS/cm^2}$, 
        $V_{\Rm{Na}} = 55\, \Rm{mV}$, $\phi_{n} = \frac{200}{7}$,}\\\rowcolor{LightGray}
        \multicolumn{8}{p{36.5em}}{
        $\sigma_{\Rm{K}} = 10\, \Rm{mV}$, $V_{\Rm{Na(P)}} = 55\, \Rm{mV}$,
        $\sigma_{\Rm{Na(P)}} = -5\, \Rm{mV}$, $g_{\Rm{Na(P)}} = 9 \,
        \Rm{mS/cm^2}$}
        \\\thickhline
    \end{tabular}
    \caption{\bfseries \sffamily Simulation Parameters}
    \label{Table:5}
\end{table}
%%

@@

We simulated the model described in Table~\ref{Table:4} using parameters
given in Table~\ref{Table:5} and the corresponding inputs (see 
Table~\ref{Table:3}). First, we examined the response of the present 
implementation to rhythmic hyperpolarization. In \cite{wang:1994} this is 
illustrated in Wang's Fig~$1$. Thus, we applied a periodic current pulse of
$-1\,\Rm{\mu A/cm^2}$ amplitude at several different frequencies
($\frac{1}{P_0}$ is the frequency in $\Rm{Hz}$ and $P_0$ is the corresponding
period in $\Rm{ms}$) ranging from $0.1\,\Rm{Hz}$ to $15\,\Rm{Hz}$ with a 
resolution (discretization) of $100$ samples. The same number of samples used 
for discretizing the duration (ON/OFF) of the pulse for each frequency. The ON
duration of a pulse is defined by the value of $p$ and the OFF duration as
$P_0 - p$.

The results are depicted in Figure~\ref{Fig:2}. Upper panel shows two different
simulations of the present implementation at specific frequencies 
($5,\, 0.5\, \Rm{Hz}$) and ratios $p/P_0$ ($0.6, 0.6$), respectively (following
the upper panels of Fig~$1$ in \cite{wang:1994}). The results in
Figure~\ref{Fig:2} are comparable to the ones presented in \cite{wang:1994}
and the timescales are exactly the same ($400\, \Rm{ms}$ for the left sub-panel
and $4\, \Rm{s}$ for the second one). However, numbers regarding pulse ON 
duration ($p$) in Wang's Fig~$1$ are possibly an error. As an example, assume
that the frequency is $\frac{1}{P_0} = 5\, \Rm{Hz}$ and $\frac{p}{P_0} = 0.6$
then the pulse ON duration must be $p = 120\, \Rm{ms}$ and not $160\, \Rm{ms}$ 
(that is reported in \cite{wang:1994}). Bottom panel illustrates the total 
results of $100 \times 100$ simulations. In order to create this figure, we
counted the number of spikes, both supra- and sub-threshold ones, generated per
pulse and then we computed the mean (this procedure is not described 
in full detail in \cite{wang:1994}, however more details can be found in
\cite{mccormick:1990}). Figure~\ref{Fig:2} differs from the one in 
\cite{wang:1994}, to the point that the shaded area that contains an average
number of spikes below $1.0$ (but not 
zero) is larger than in \cite{wang:1994}. Unfortunately, there are not enough
details regarding Fig~$1$ in \cite{wang:1994} to make a faithful reproduction
of that figure.

%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure2.pdf}
    \caption{{\bfseries \sffamily Responses to rhythmic hyperpolarizations.}
    We stimulate the model given in Table~\ref{Table:4} using a periodic pulse
    with frequency ($\frac{1}{P_0}$) varying from $0.1$ to $15\, \Rm{Hz}$.
    {\bfseries \sffamily Upper panels} show the results of two simulations out
    of $100 \times 100$. The blue curve indicates bursts of four spikes
    ($\frac{1}{P_0} = 5\, \Rm{Hz}$ and $\frac{p}{P_0} = 0.6$). Black curve
    depicts a case of two spikes bursts ($\frac{1}{P_0} = 0.5\, \Rm{Hz}$ and
    $\frac{p}{P_0} = 0.6$).
    {\bfseries \sffamily Bottom panel} shows the average number of spikes (sub-
    or supra-threshold) measured per pulse. Frequency varies in the interval 
    $[0.1, 15]\, \Rm{Hz}$ and the ratio $\frac{p}{P_0}$ is in interval $[0, 1]$.
    Numbers signify the average number of spikes per pulse.}
    \label{Fig:2}
\end{figure}
%%

The next simulation investigated the transition from subthreshold to bursting
oscillations via chaos. This is illustrated in Fig~$3$ in \cite{wang:1994}. In
this case a steady current is applied to the model described in
Table~\ref{Table:4}. In \cite{wang:1994} Wang used eleven different
amplitudes for the constant current in order to explore the model's behavior
repertoire. Hence, 
$$I_{\text{app}} = 
3.0, 0.0, -0.45, -0.455, -0.47, -0.55, -0.6, -0.8, -1.3, -1.4, -2.0\, 
\Rm{\mu A /cm^2}.$$
The results for these simulations are depicted in Figure~\ref{Fig:3}. In this
case, there was no difference between the present implementation and the
original one.
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.\textwidth]{figs/Figure3.pdf}
    \caption{{\bfseries \sffamily Dynamic behavior of neuron.} 
    Eleven different external constant currents $I_{\text{app}} = 
    3.0, 0.0, -0.45, -0.455, -0.47, -0.55, -0.6, -0.8, -1.3, -1.4, -2.0\, 
    \Rm{\mu A /cm^2}$ have been applied as inputs to the model described by
    equations given in Table~\ref{Table:4}. The behavior of the model spans
    from tonic spiking to spikes bursts, subthreshold activity and no activity 
    at all.}
    \label{Fig:3}
\end{figure}
%%

\cite{wang:1994} has showed that the current model expresses a hysteresis
(see Wang's Fig~$4$). In order to reproduce that case we simulated
the model using a constant external current $I_{app}$. The simulation starts
by applying a current with an amplitude of $-0.433\, \Rm{\mu A / cm^2}$ and 
continues by increasing the amplitude up to $-0.55 \mu A /cm^2$. At every 
iteration, sub- and/or supra-threshold activity of the membrane potential is 
detected. The results are given in Figure~\ref{Fig:4} {\bfseries \sffamily A}. 
%%
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/Figure4.pdf}
    \caption{{\bfseries \sffamily Hysteresis near the transition from the
    subthreshold to bursting oscillation.} ({\bfseries \sffamily A})
    Hysteresis diagram indicates a coexistence of bursting and subthreshold 
    activity. ({\bfseries \sffamily B}) Bistability example
    shows how the same system can produce either subthreshold activity (black
    curve) or burst activity (gray curve). ({\bfseries \sffamily C}) shows the
    activation of $H$ for the same simulation as in the 
    panel above. ({\bfseries  \sffamily D}) A brief current pulse at
    $0.25\, \Rm{\mu A /cm^2}$ (black curve) or $-1.2\, \Rm{\mu A/cm^2}$ (gray
    curve) followed by a steady current at $-0.47\, \Rm{\mu A/cm^2}$ is used 
    as external input to the model. }
    \label{Fig:4}
\end{figure}
%%
In addition, the model expresses a bistability. This was tested by applying the
same protocol as in \cite{wang:1994}. Thus first a brief pulse 
(for $100\, \Rm{ms}$) of $0.25\, \Rm{\mu A /cm^2}$ (black line in
Figure~\ref{Fig:4} {\bfseries \sffamily C}) or $-1.2\, \Rm{\mu A/cm^2}$ (gray
line in Figure~\ref{Fig:4} {\bfseries \sffamily C}) is applied to the model
followed by a steady current at $-0.47\, \Rm{\mu A /cm^2}$. Such a protocol
causes the state of the model to switch from purely sub-threshold to mixed
sub- and suprathreshold. These results are illustrated in
Figure~\ref{Fig:4} {\bfseries \sffamily B}. In
the same figure panels {\bfseries \sffamily C} and {\bfseries \sffamily D}
depict the input to the model and the $H$ of the Sag channel, respectively.
